State of the Art in Scientific Workflow Systems

### 2014-05-30 paper.tex
provenance desc

\item \textbf{Provenance and MetaData.} Historical data and metadata has been
crucial entities in many research fields. They help connecting results from
a multitude of research points of view. A provenance trace of a computation can
help checkpoint methods and reproduce and modify partial computation. Automated
observations of deviations in scientific phenomena from provenance data is one
of the key triggers for new scientific discoveries. Fields of studies involving
genomic and protiens are examples of domains where provenance and metadata
plays key roles. SWEs can be integrated or extended with metadata and
provenance techniques rendering powerful computing and traceability features.

>>>>

\item \textbf{Provenance and MetaData.} Historical data and metadata has been
crucial entities in many research fields. They help connecting results from
a multitude of research points of view. A provenance trace of a computation can
help checkpoint methods and reproduce and modify computation fully or
partially. Automated observations of deviations in scientific phenomena from
provenance data is one of the key triggers for new scientific discoveries.
Fields of studies involving genomic and protiens are examples of domains where
provenance and metadata plays key roles. SWEs can be integrated or extended
with metadata and provenance techniques rendering powerful computing and
traceability features. In fact, most SWEs of today have separate modules or
extensions for handling provenance and/or metadata.
